Paper on the carbonate chemistry at Ny-Ålesund

### 2020-12-19 paper.Rmd
nothing

```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}
zz <- d %>%
  group_by_key() %>%
  index_by(quarter = ~ quarter(.)) %>% # monthly aggregates
  summarise(
    sal_fb_na = sum(!is.na(sal_fb))/n())
zz

>>>>

```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}
zz <- d %>%
  group_by_key() %>%
  index_by(quarter = ~ quarter(.)) %>% # monthly aggregates
  summarise(
    sal_fb_na = sum(!is.na(sal_fb))/n())
